%-------------------------
% Resume in Latex
% Author : Adam Galek
% Based off of: https://github.com/jakegut/resume
% Which was based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Adam Galek} \\ \vspace{1pt}
    \small 647-219-8131 $|$ \href{mailto:galekxy94@gmail.com}{\underline{galekxy94@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/adamgalek/}{\underline{linkedin.com/in/adamgalek/}} $|$
    \href{https://github.com/TheGalekxy}{\underline{github.com/TheGalekxy}}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{Sep 2021 -- Present}
      {Xello}{Toronto, ON - Remote}
      \resumeItemListStart
        \resumeItem{Developed an internal component library using Lit, TypeScript, and Sass, creating over 25 components utilized by five product teams.}
        \resumeItem{Created and implemented accessibility guidelines for the Xello Design System component library, including pre-commit accessibility linting to improve standards and developer efficiency.}
        \resumeItem{Improved the design-to-development workflow by establishing a process for adding, updating, and utilizing icons and illustration assets in product applications, enhancing UI consistency and ease of use for developers and designers.}
        \resumeItem{Automated the creation of a global style file using Sass and design tokens, ensuring UI consistency across Xello’s applications.}
        \resumeItem{Conducted training sessions to enhance stakeholders' knowledge of the company's internal tools.}
        \resumeItem{Developed tooling with C\#, SQL, and ASP.NET to support content stakeholders, enabling efficient connection to source data and streamlined creation, editing, and deletion of data.}
        \resumeItem{Led the end-to-end development of an automated data pipeline to integrate external data into internal systems. Implemented robust error handling, unit and integration testing, and failure notifications via email and Slack.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
    % \resumeSubSubheading
    % {UI Engineer Intern}{Jul 2021 - Sep 2021}
    % \resumeItemListStart
    %     \resumeItem{Apache Beam}
    %      {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
    % \resumeItemListEnd
    % \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Web Developer}{Jan. 2021 -- Mar. 2021}
      {Noel Semple Campaign}{Toronto, ON - Remote}
      \resumeItemListStart
        \resumeItem{Collaborated as a team of 2 developers to develop a campaign website using the Nationbuilder content management system}
        \resumeItem{Developed a political campaign website from inception to delivery on a strict deadline for campaign launch}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Humber College}{Toronto, ON}
      {Ontario Graduate Certificate, Web Development}{Sep. 2020 -- August 2021}
    \resumeSubheading
      {McMaster University}{Hamilton, ON}
      {Honours Bachelor of Arts in Anthropology, Business Studies Certificate }{Sep. 2013 -- Dec 2019}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{JustCook} $|$ \emph{HTML5, CSS, JavaScript, React, Express, Redux, Git}}{March 2021 -- May 2021}
          \resumeItemListStart
            \resumeItem{Developed a full-stack web application with a team of 4 other developers using a React frontend}
            \resumeItem{Connected to the Spoonacular API to retrieve recipe data}
            \resumeItem{Implemented a shopping cart with state management using Redux}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Galekxy Media Youtube} }{May 2020 -- Present}
          \resumeItemListStart
            \resumeItem{A YouTube Channel to explore my interests in web development, technology, and to help other programmers learn beginner web development content}
            \resumeItem{Published first video, a tutorial on how to host a static React application using GitHub pages has gained over 11000 views, 450 likes, and 60 comments}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: HTML, CSS, JavaScript, C\#, SQL, TypeScript, Sass, Htmx, PostgreSQL } \\
     \textbf{Frameworks}{: Lit, ASP.Net, React} \\
     \textbf{Other Technologies}{: Node.js, xUnit, Jest, Slack Webhooks} \\
     \textbf{Developer Tools}{: Git, VS Code, Visual Studio, SQL Server Management Studio, ChatGPT } \\
    %  \textbf{Libraries}{: pandas, NumPy, Matplotlib}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
